---
title: "ColdStorage"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup}
knitr::opts_knit$set(root.dir = 'C:/Users/Hp/Desktop/R Programming')
```

## Invoking Libraries

```{r}
library(ggplot2)
library(lattice)
library(rmarkdown)
library(dplyr)
```

## Seting up the working directory

```{r}
setwd("C:/Users/Hp/Desktop/R Programming")
getwd()
```

## Importing data

```{r}
storage <- read.csv("Cold_Storage_Temp_Data.csv")
```

## Top 15 entries on the dataset

```{r}
head(storage , 15)
```

## Bottom 15 entries of the dataset

```{r}
tail(storage , 15)
```

## Dimensions of dataset

```{r}
dim(storage)
```

## Column names of the dataset

```{r}
colnames(storage)
```

## Structure of the dataset

```{r}
str(storage)
```

## Summary of the dataset

```{r}
summary(storage)
```

## Referencing column names without $ 

```{r}
attach(storage)
```

## Summary of dataset grouped by indices/factor "season" 

```{r}
by(storage, INDICES = Season, FUN = summary)
```

## Mean temperature in rainy season

```{r}
RainySeason <- storage[Season == "Rainy", ]
mean(RainySeason$Temperature)
```

## Mean temperature in summer season

```{r}
Summerseason <- storage[Season == "Summer", ]
mean(Summerseason$Temperature)
``` 

## Mean temperature in winter season 

```{r}
Winterseason <- storage[Season == "Winter", ]
mean(Winterseason$Temperature)
```

## Overall mean temperature for the entire year 

```{r}
Mean <- mean(Temperature)
Mean
```

## Standard Deviation of temperature for the entire year
 
```{r}
StandardDeviation <- sd(Temperature)
StandardDeviation
```

## Maximum & Minimum temperature in a year

```{r}
max(Temperature)
min(Temperature)
```

## Univariate Analysis

```{r}
boxplot(Temperature , xlab = "Temperature in Deg C" , main = "Boxplot of Temperature" , col = "Blue",
        horizontal = TRUE)
hist(Temperature, xlab = "Temperature in Deg C", col = "Blue")
```

## Univariate Analysis using ggplot2

```{r}
qplot(Temperature, data = storage , geom = "density" , fill = Season,  xlab = "Temperature in Deg C" , ylab = "Freuency") + ggtitle("Density Frequency of Temp by Season") + theme(plot.title = element_text(hjust = 0.5)) + geom_density(alpha =0.8)

ggplot(storage, aes(x = Temperature, fill = Month, alpha = 0.2)) + geom_density() + ggtitle("Density of Temperature monthly") + theme(plot.title = element_text(hjust = 0.5))

qplot(Temperature, data = storage  , fill = Season, 
      xlab = "Temperature in Deg C" , ylab = "Freuency") + ggtitle("Density Frequency of Temp by Season") + theme(plot.title = element_text(hjust = 0.5)) + geom_bar()    
```


## Bivariate Analysis 

```{r}
boxplot(Temperature~Season , col = c("red","green","blue"), horizontal = TRUE ,
        xlab = "Temperature in Deg C", ylab = "Season")
ggplot(storage, aes(x = Season, y = Temperature, fill = Month)) + geom_boxplot() + ggtitle("Boxplot distribution of season for temperature") + theme(plot.title = element_text(hjust = 0.5))
ggplot(storage, aes(x = Month, y = Temperature, fill = Season  )) + geom_boxplot() + ggtitle("Boxplot representation of Months for Temperture") + theme(plot.title = element_text(hjust = 0.5))
```


## Probability of temperature falling below 2 deg C

```{r}
pnorm(2,Mean,StandardDeviation)
```

## Probability of temperature going above 4 deg C

```{r}
1 - pnorm(4,Mean,StandardDeviation)
```

